### 2016-11-16 paper/modes.tex
updated listing and some descriptions about par modes

\begin{itemize}
\item \textbf{Sequential (\Seq).}~This configuration results in
    sequential execution of test classes and their methods, according
    to a given order defined in the testing framework (\eg, the order
    of methods returned by Java Reflection
    API)~\cite{junit-test-order}. For JUnit, this is the default
    configuration.

\item \textbf{Sequential classes; parallel methods
  (\ParClassSeqMeth{}).} This configuration results in the sequential
  execution of the test classes assigned to the JVM.  However, within
  each class, test methods run in parallel. In JUnit,
  \emph{ParallelComputer} provides support to parallel execution; it
  instantiates a test runner with a \emph{ExecutorService} from the
  Java Concurrent API. Each test method is executed in a separated
  thread as the thread pool creates new threads on-demand and reuse
  them if any thread is available.

\Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}

\item \textbf{Parallel classes; sequential methods
  (\SeqClassParMeth{}).}  This configuration results in the parallel
  execution of test classes but test methods of any given class are
  executed sequentially. As in \ParClassSeqMeth, the runner has a
  cached thread poll. However, instead of executing test methods from
  a single test class, the test suite runner executes classes in
  separated threads and methods in sequence within each thread.

\item \textbf{Parallel methods (\ParClassParMeth).} This configuration
  results in parallel execution of any given test method of any class.
  \Jbc{I need to confirm this but AFAIK this is how it happens}
  It is the union of \ParClassSeqMeth and \SeqClassParMeth: there is a
  thread pool for execution classes on separated threads and within
  each test class, there is a runner with a \emph{ExecutorService} to
  run test methods in parallel.
\end{itemize}

@@

\begin{figure}[h!]
    \centering
    \lstset{language=XML}
    \begin{lstlisting}
    <plugin>
        <groupId>org.apache.maven.plugins</groupId>
        <artifactId>maven-surefire-plugin</artifactId>
        <configuration>
            <parallel>methods</parallel>
            <threadCount>2</threadCount>
            <perCoreThreadCount>true</perCoreThreadCount>
        </configuration>
    </plugin>
    \end{lstlisting}
    \caption{\label{fig:surefire}\Fix{...}}
\end{figure}

>>>>

\begin{itemize}
\item
    \textbf{Sequential (\Seq).}~This configuration results in
        sequential execution of test classes and their methods,
        according to a given order defined in the testing framework
        (\eg, the order of methods returned by Java Reflection
        API)~\cite{junit-test-order}. For JUnit, this is the default
        configuration.
\item
    \textbf{Sequential classes; parallel methods
        (\ParClassSeqMeth{}).}~This configuration results in the
        sequential execution of the test classes assigned to the JVM.
        However, within each class, test methods run in parallel. In
        JUnit, \emph{ParallelComputer} provides support to parallel
        execution: it instantiates a test runner with an
        \emph{ExecutorService} from the Java Concurrent API. Each test
        method is executed in a separated thread as the thread pool
        creates new threads on-demand and reuse them if any thread is
        available.
    \Comment{http://junit.org/junit4/javadoc/latest/src-html/org/junit/experimental/ParallelComputer.html#line.14}
\item
    \textbf{Parallel classes; sequential methods
        (\SeqClassParMeth{}).}~This configuration results in the
        parallel execution of test classes and sequential test
        methods. As in \ParClassSeqMeth, the test runner has a cached
        thread poll but instead of executing test methods from a
        single test class, the test suite runner executes classes in
        separated threads and methods sequentially within each thread.
\item
    \textbf{Parallel methods (\ParClassParMeth).}~This configuration
        results in the parallel execution of any test method from any
        class.  \Jbc{I need to confirm this but AFAIK this is how it
        happens} As in \SeqClassParMeth, classes execute on separated
        threads but test methods are also executed in parallel. More
        precisely, there is a thread pool to execute classes in
        separated threads (\ie, like in \ParClassSeqMeth) and, within
        each class runner, there is an \emph{ExecutorService} to run
        test methods in parallel (\ie, like in \SeqClassParMeth).
\end{itemize}

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <parallel>methods</parallel>
        <threadCount>2</threadCount>
        <perCoreThreadCount>true</perCoreThreadCount>
    </configuration>
</plugin>
\end{lstlisting}
\caption{\label{fig:surefire} Example of Maven Surefire configuration:
    test methods in parallel (\emph{parallel} parameter) using two
    threads (\emph{threadCount} parameter) per core (boolean flag
    \emph{perCoreThreadCount}).}
\end{figure}
